% Title: PS Ma Zhong
%% Author: Ma Zhong / darkness301@me.com
%% Created: 2018-07-09
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%
%% How to Compile:
%%     $ xelatex Personal Statement.tex
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper]{article}
\usepackage[letterpaper,margin=1.5in,noheadfoot]{geometry}
\usepackage{fontspec, color, enumerate, sectsty}
\usepackage[normalem]{ulem}

% empty page numbers
\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                      YOUR INFORMATION
%
%      PLEASE EDIT THE FOLLOWING LINES ACCORDINGLY!!
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\pstitle}{Personal Statement}
\newcommand{\yourname}{Ma Zhong}
\newcommand{\youremail}{darkness301@me.com}

%% FONTS SETUP
\defaultfontfeatures{Mapping=tex-text}
\setromanfont[Scale=1.0]{Helvetica Neue Light}
\setmonofont[Scale=0.8]{Helvetica Neue Light}
\setsansfont[Scale=0.9]{Helvetica Neue Light}
\newcommand{\amper}{{\fontspec[Scale=.95]{Helvetica}\selectfont\itshape\&~{}}}
\usepackage[bookmarks, colorlinks, breaklinks,
	pdftitle={\yourname - \pstitle},pdfauthor={\yourname}, unicode]{hyperref}
\hypersetup{linkcolor=magneta,citecolor=magenta,filecolor=magenta,urlcolor=[named]{WildStrawberry}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%ß
%                      Title and Author Name
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\begin{center}{\huge \scshape \bfseries \pstitle}\end{center}
\begin{center}\vspace{0.2em} {\Large \yourname\\}
	{\youremail}\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                      PS Body
% NOTE: Use \amper instead of \&
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
My major interests and passions are Computer Science and Maths. So,
after completing my undergraduate education in Northeastern University
at Qinghuangdao, China in the field of Computer Science and Technology,
I had got my master's degree in Computer Science from University of Electric
Science and Technolgy of China.\vspace{4pt}

My primary interests in computer science are Cryptology, Cybersecurity and 
Artificial intelligence. My master's course ``Number Theory'' kindled my 
interest in Cryptology. During follwoing intern project ``SSL protocoal'', I did 
Research on cryptology algorithms including Symmetric-key algorithms, Public-key 
algorithms, Digest algorithms, pre-random generation algorithm, Implementing 
SSL protocol on KCXP which was a communication middle-ware and finally I 
Integrated SSL protocol and these cryptology algorithms. The project taught me a 
great deal about Cryptology and Network security. the ``Padlock SDKs'' project 
which was developing a sets of SDKs providing faster and more effective cipher 
suites based on cryptographic acceleration CPU instructions built in rather than 
the software implementation had deepend my understanding of Cryptology and 
allowed me see it from another perspective.\vspace{4pt}

Meanwhile, I had developed ``SIP Phone SDKs'' project, a set of SDKs for 
constructing a VoIP call, had given me the opportunity to be familar with 
Network Communication and SIP(Session Initiation Protocol) protocol family. 
The follwoing five years, I mainly worked on embedded systems, mainly mobile 
phone as a senior software engineer and technical leader. This unique experience 
enriched me with broad knowledge in Computer Science and has given me insights of 
the Computer Science field.\vspace{4pt}

Howerver, the birth of my son broke my about 10 years career in computer. I had to 
become successively a National Civil Servant and a self-employed worker in order 
to take care my child. But my enthusiasm on computer secince has never been 
extinguished. Now, my son has entered the nursery school and It is the good 
opportunity for me to reshape my carreer. Due to the long term leaving of the 
computer area, I think that it is a good idea to participate the postgraduate 
study, which can refresh my knowledge and skills related to Computer Science.
Revisiting the education system with the insights will give me a better 
ability to reshape my career by making sure I will have he ability absorb the 
knowledge better.\vspace{4pt}

I plan to participate Postgraduate Diploma Programme about Cybersecurity and 
Artificial Intelligence in graduate school. As UC have the famous Intelligent 
Computer Tutoring and Cybersecurity groups I feel that UC is the ideal place 
to study these fields. Additionally, UC offers an excellent selection of courses and
supports a vigorous research program in my areas of interest. I beleive UC is my 
best choice.\vspace{4pt}

After receiving a PgDip., if possible, I plan to pursue a Ph.D or an academic 
career in computer science research.\vspace{4pt}

\end{document}
