%-------------------------
% Resume in Latex
% Author : Ma Zhong
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{fontspec}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\defaultfontfeatures{Mapping=tex-text}
\setromanfont[Scale=1.0]{Helvetica Neue Light}
\setmonofont[Scale=0.8]{Helvetica Neue Light}
\setsansfont[Scale=0.9]{Helvetica Neue Light}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
	\textbf{{\huge Ma Zhong}} & Email : \href{mailto:darkness301@me.com}{darkness301@me.com}\\
	Address : 37 Anming Road, Pidu District, Chengdu, Sichuan, China 611730 & Mobile : +86-186-1579-5536 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{\textbf{Education}}
\resumeSubHeadingListStart
\resumeSubheading
{University of Electric Science and Technology of China}{Chengdu, China}
{Master of Engineering in Computer System Architecture;  GPA: 3.12/4.0}{Sep. 2002 -- Jun. 2005}
\resumeSubheading
{Northeastern University at Qinghuangdao}{Qinghuangdao, China}
{Bachelor of Engineering in Computer Science and Technolog}{Sep. 1998 -- July. 2002}
\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{\textbf{Experience}}
\resumeSubHeadingListStart
\resumeSubheading
{Self-employed}{Chengdu, China}
{Entrepreneur \& Househusband}{Jan. 2016 - Present}
\resumeItemListStart
\resumeItem{Three Cooperation Human Resources Service(Chengdu) Co.,Ltd.}
{It is a company which mainly provides labour dispatch products. Helped to establish the company.}
\resumeItem{Childcare}
{Look after my son at home.}
\resumeItemListEnd

\resumeSubheading
{Human Resources and Social Security Bureau of Pixian County}{Chengdu, China}
{National Civil Servant}{May  2013 - Dec. 2015}
\resumeItemListStart
\resumeItem{Civil Servant Management System}
{It is a personnel management system based on web.}
\resumeItemListEnd

\resumeSubheading
{Spreadcomm Technology Corp.}{Chengdu, China}
{Technical leader}{Jun. 2011 - Apr. 2013}
\resumeItemListStart
\resumeItem{Technical support}
{Sloved problmes about SIP, TCP/IP, Network security and trained junior software engineers on VoIP, Cryptology or other areas.}
\resumeItemListEnd

\resumeSubheading
{Teleca Solution Co.,Ltd.}{Chengdu, China}
{Senior Software Engineer}{Nov. 2008 - May  2011}
\resumeItemListStart
\resumeItem{MCE/MCC}
{MCE/MCC is a Middleware Software of Symbian which provides IP service for application.i.e PoC, VoIP, MuSh.}
\resumeItem{Technical Support}
{Solved problmes about SIP, RTP, NAT, SVP, Cryptology or other componets.}
\resumeItemListEnd

\resumeSubheading
{COMMIT Inc.}{Shanghai, China}
{Senior Software Engineer}{Jun. 2007 - Apr. 2008}
\resumeItemListStart
\resumeItem{Video Telephony}
{Video Telephony is a videophone based on TD-SCDMA, one of 3G standards. Maintained Radvision 3g324m protocol stack. Integrated CM324 module and 3g324m protocol stack.}
\resumeItem{DTI module}
{Developed and maintained DTI module. Established DTI channels between CM324 module and Speech module, and between CM324 module and OpenMax module.}
\resumeItemListEnd

\resumeSubheading
{S3 Graphics Inc.}{Shanghai, China}
{Senior Software Engineer}{Feb. 2006 - Jun. 2007}

\resumeSubheading
{VIA Software Co.,Ltd.}{Hangzhou, China}
{Software Engineer}{Apr. 2005 - Feb. 2006\vspace{4pt}}

{VEPD(VIA Embedded Platform Department) had been transfered to Shanghai from Hangzhou on Feb. 2006.\vspace{-4pt}}
\resumeItemListStart
\resumeItem{SIP Phone SDK}
{SIP Phone SDK is a set of SDKs for constructing a VoIP call. Implemented SIP protocol(Parser, Transaction \& FSM, UA), SRTP protocol, Key management module, Transport(UDP, TCP, TLS) layer, Phone Toolkit layer, key mapping module on Windows, Linux and Windows mobile platforms.}
\resumeItem{PadLock SDK}
{Padlock SDK is a set of SDKs providing more effective cipher suites. Encapsulated random generator assembly instruction, Hash algorithm assembly instruction and AES algorithm assembly instructions by C language. Implemented mode exponent interface basing on mode multiplication assembly instruction.}
\resumeItemListEnd

\resumeSubheading
{Shenzhen Kingdom Sci-Tech Co.,Ltd.}{Shenzhen, China}
{Intern Software Engineer}{Jun. 2003 - Jan. 2004}
\resumeItemListStart
\resumeItem{Cryptology Research}
{Research on cryptology algorithms including Symmetric-key algorithms: DES, RC2, RC5, AES, IDEA, Public-key algorithms: RSA, DH, ECC and Digest algorithms: SHA, MD5. Designed a pre-random generation algorithm.}
\resumeItem{SSL protocol}
{Implemented SSL protocol on KCXP which was a communication middle-ware. Integrated SSL protocol and these cryptology algorithms.}
\resumeItemListEnd

\resumeSubHeadingListEnd


%-----------PROJECTS-----------------
%\section{Projects}
%  \resumeSubHeadingListStart
%    \resumeSubItem{QuantSoftware Toolkit}
%      {Open source python library for financial data analysis and machine learning for finance.}
%    \resumeSubItem{Github Visualization}
%      {Data Visualization of Git Log data using D3 to analyze project trends over time.}
%    \resumeSubItem{Recommendation System}
%      {Music and Movie recommender systems using collaborative filtering on public datasets.}
%    \resumeSubItem{Mac Setup}
%      {Book that gives step by step instructions on setting up developer environment on Mac OS.}
%  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{\textbf{Programming Skills}}
\resumeSubHeadingListStart
\item{
            \textbf{Languages}{: C/C++, Python, Scheme, Java}
            \hfill
            \textbf{Technologies}{: Network, VoIP, Cryptology }
      }
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
